### 2013-07-20 paper.tex
2nd milestone.

% TODO change this
We then do a bunch of nonsense.

\section{Preliminaries and Definitions}
\subsection{An Extended Introduction}
\label{sec:prelim}
% \subsection{Coxeter Rings, and the Bott-Samelson Bimodules}
Let $W$ be a group with two generators $s$ and $t$ corresponding to reflecting over two hyperplanes in a real Euclidean space $V$, and let $\alpha_s$ and $\alpha_t$ be unit vectors normal to these planes.  We will assume that the angle formed by $\alpha_s$ and $\alpha_t$ is not a rational multiple of $\pi$, so that the order of $st$ in $W$ is infinite.  If $V$ has a positive definite symmetric bilinear form $(\mu, \lambda)$, then each $v \in V$ is reflected via the map \[ v \mapsto v - \frac{2(v,a)}{(a,a)} a. \]  In particular, $s(\alpha_s) = -\alpha_s$ and $t(\alpha_t) = -\alpha_t$.  Furthermore, we see that there exist fixed constants $x$ and $y$ such that
\begin{align*}
	s(\alpha_t) &= \alpha_t + x \alpha_s \\
	t(\alpha_s) &= \alpha_s + y \alpha_t
\end{align*}
Now we define the \emph{Coxeter ring} by $R = \RR[\alpha_s, \alpha_t]$.  Then $W$ acts on $R$ by precisely the same algorithm as described above.

@@

Furthermore, one can again verify that $\barbell{barbell_blue}$, when on the far left, is simply $\alpha_s$.

@@

Further details on the evaluation of these maps are detailed in section \ref{sec:explain_poly_eval}, but before that we need to introduce certain definitions for clarity.

@@

\begin{definition*}
	A \emph{fence} is a contiguous path which runs from the top of the boundary to the bottom of the boundary (i.e. paths between the labelled vertices).  The diagram is divided by these fences into \emph{pastures}, which will be numbered from left to right as $0$, $1$, \dots, $k$, where $k$ is the number of fences.
\end{definition*}

We remind the reader that we are working modulo lower terms; any map which contains a ``half fence'' (i.e. a connected component which touches a boundary exactly once) is not considered.

@@

\begin{definition*}
	A \emph{bubble} is a bounded face alongside with any components contained within it, which are its \emph{contents}.  
\end{definition*}

@@

\begin{definition*}
	A \emph{caterpillar} is any connected collection of bubbles.
\end{definition*}

\subsection{Representations of Maps as Polynomials}
% TODO actually do this

\section{One-Color Case: Characterizing $\MM_{\SS_n}(\ul a, \ul b)$}
In this section we provide a complete characterization for the $\MM_{\SS_n}(\ul a, \ul b)$.  The proof is effectively trivial, but requires some rather irritating details and definitions in order to be clear.

@@

\section{Constraints on the Diagrammatics in the Alternating Case}
\label{sec:caterpillar}
We now turn our attention to the case of $\ul r = \AA_n$.

In this section we will show several results which show that the possible outputs of a map with base $\AA_n$ are extremely restricted.  We present them below, before providing proofs of each.
\begin{lemma}[Bubble Lemma]
	Consider a bubble in a full-diagram with base $\AA_n$.  The contents of the bubble are either a barbell or a caterpillar.
\end{lemma}
\begin{corollary}[Caterpillar Corollary]
	A caterpillar in a full-diagram with base $\AA_n$ evaluates as 
\end{corollary}<++>

>>>>

TODO: Add road map once I figure out what results I actually have

\section{Preliminaries and Definitions}
NOTE: If possible, this document should be printed in color.  However, I have left blue lines as solid and red lines as dotted for readability.

\subsection{An Extended Introduction}
\label{sec:prelim}
% \subsection{Coxeter Rings, and the Bott-Samelson Bimodules}
Let $W$ be a group with two generators $s$ and $t$ corresponding to reflecting over two hyperplanes in a real Euclidean space $V$, and let $\alpha_s$ and $\alpha_t$ be unit vectors normal to these planes.  We will assume that the angle formed by $\alpha_s$ and $\alpha_t$ is not a rational multiple of $\pi$, so that the order of $st$ in $W$ is infinite.  If $V$ has a positive definite symmetric bilinear form $(\mu, \lambda)$, then each $v \in V$ is reflected via the map \[ v \mapsto v - \frac{2(v,a)}{(a,a)} a. \]  In particular, $s(\alpha_s) = -\alpha_s$ and $t(\alpha_t) = -\alpha_t$.  Furthermore, we see that there exist fixed constants $x$ and $y$ such that
\begin{align*}
	s(\alpha_t) &= \alpha_t + x \alpha_s \\
	t(\alpha_s) &= \alpha_s + y \alpha_t
\end{align*}
Now we define the \emph{Coxeter ring} by $R = \RR[\alpha_s, \alpha_t]$.  Then $W$ acts on $R$ by precisely the same algorithm as described above.

@@

% Furthermore, one can again verify that $\barbell{barbell_blue}$, when on the far left, is simply $\alpha_s$.

@@

Further details on the evaluation of these maps are detailed in section \ref{sec:prelim_explain_poly_eval}, but before that we need to introduce certain definitions for clarity.

@@

\begin{definition*}
	A \emph{fence} is a contiguous path which runs from the top of the boundary to the bottom of the boundary (i.e. paths between the labelled vertices).  The diagram is divided by these fences into \emph{pastures}, which will be numbered from left to right as $0$, $1$, \dots, $k$, where $k$ is the number of fences.  
\end{definition*}
\begin{definition*}
	A component is called \emph{attached} if it is connected to a fence.  Otherwise, it is \emph{free}.  By convention, any attached components belong to the pasture to the left of the associated fence.
\end{definition*}

% We remind the reader that we are working modulo lower terms; any map which contains a ``half fence'' (i.e. a connected component which touches a boundary exactly once) is not considered.

@@

\begin{definition*}
	A \emph{bubble} is a bounded face alongside with any components contained within it, which are its \emph{contents}.  The color of the bubble is the color of the edges which form the bounded face.
\end{definition*}

@@

\begin{definition*}
	A \emph{caterpillar} is any connected component for which each edge belongs to some bubble (in the caterpillar).  The \emph{size} of the caterpillar is the number of bubbles it is composed of.
\end{definition*}

Notice that every free component can be expressed as a collection of caterpillars joined by edges.  Furthermore, every attached component can be described as a free component attached by edges to a fence.

\subsection{Representations of Maps as Polynomials}
\label{sec:prelim_explain_poly_eval}

In order to study these maps as algebraic structures, we wish to consider full-maps as polynomials in $\RR[x,y][\alpha_s,\alpha_t]$.  Hence, we establish the following conventions:
\begin{enumerate}
	\ii The map $x \mapsto fx$ will be abbreviated as $f$ from this point forward.  
	\par Note that, in particular, $\barbell{barbell_blue} = \alpha_s$.  Furthermore, one can check that, say, $\barbell{barbell_blue}\barbell{barbell_blue}\barbell{barbell_red}\barbell{alpha_blue} = \alpha_s^2 \alpha_t$.  
	Please note that $x \mapsto xf$ does not get a similar abbreviation.  So, $\barbell{alpha_blue}\barbell{barbell_blue} \neq \alpha_s$.
	\ii We will work \emph{modulo lower terms}.  That is, any map which contains a connected component that touches any boundary only once (total) is considered zero.  So, for example, $\barbell{break_blue} = 0$.
\end{enumerate}
Henceforth, we will refer to diagrams and their associated polynomials interchangeably.

One can verify that, using the barbell-forcing rules, we can recursively move all barbells to the right, and any ``broken'' walls are reduced to zero, or are contracted.  Hence, any full-diagram can be reduced to linear combinations of maps of the form $x \mapsto \alpha_s^m \alpha_t^n x$.  In other words, every full diagram can be represented as a polynomial in $\RR[x,y][\alpha_s,\alpha_t]$.

In fact, we can even show that, with this new convention, that the following identity holds for every $f$:
\begin{equation}
	\barbell{alpha_blue} f = \partial_s(f) \barbell{break_blue} + s(f) \barbell{alpha_blue}
	\label{eq:barbell_break}
\end{equation}
where $\partial_s$ is the Demazure operator defined in section \ref{sec:prelim_genrel}.

The problem statement then becomes to compute the polynomial $\MM_{\ul r}(\ul a, \ul b)$ with a formula in terms of $\ul r$, $\ul a$, $\ul b$.

\section{A Complete Characterization of the One-Color Case}
In this section we provide a complete characterization for the $\MM_{\SS_n}(\ul a, \ul b)$.  The proof is effectively trivial, but requires some rather irritating details and definitions in order to be clear.

@@

\section{Constraints in the Alternating Case}
We now turn our attention to the case of $\ul r = \AA_n$.

In this section we will show several results which show that the possible outputs of a map with base $\AA_n$ are extremely restricted.  We present them below, before providing proofs of each.
\begin{lemma}[Bubble Lemma]
	Consider a bubble in a full-diagram with base $\AA_n$.  The contents of the bubble are either a barbell or a caterpillar.
\end{lemma}
\begin{corollary}[Caterpillar Corollary]
	Any caterpillar in a full-diagram with base $\AA_n$ evaluates in the form $x^my^n\alpha_s$ if it is blue, or $x^my^n\alpha_t$ is red.
\end{corollary}
\begin{theorem}[Pasture Theorem]
	Consider a full-diagram with $N+1$ pastures with base $\AA_n$, numbered $0$, $1$, \dots, $N$, where $N \ge 1$.  Then
	\begin{enumerate}[(i)]
		\ii Pastures $1$ to $N-1$ contain no free components and at most one attached component.
		\ii Pasture $N$ contains at most one free component, either a caterpillar or a barbell.
	\end{enumerate}
\end{theorem}

TODO: Work out details of the proofs.

\section{A Recursion for the Alternating Case}
